DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
improved abstract and introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
%
We present an automated MATLAB Toolbox, named \emph{DSSynth} (Digital-System
Synthesizer), to synthesize sound digital controllers for physical plants
that are represented as linear time-invariant systems with single input and
output.  In~particular, DSSynth synthesizes digital controllers that are
sound w.r.t.~stability and safety specifications.  DSSynth considers the
complete range of approximations, including time discretization,
quantization effects and finite-precision arithmetic (and its rounding
errors).  The resulting toolbox enables the application of program synthesis
to real-world control engineering problems.
%
\end{abstract}

@@

Control theory targets the construction of reliable systems by providing
mathematical guarantees about the stability and the desired performance of
closed-loop dynamics, where outputs of discrete plant $G(z)$ are fed back
and compared to a reference signal towards which a controller $C(z)$ should
steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
depicts a typical closed-loop digital control system.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System}
\label{fig:typical-control-system}
\end{figure}

@@

The present tool paper addresses this limitation and describes a MATLAB
toolbox for DSSynth.  MATLAB is very commonly used for modeling physical
plants.  Thus, the integration into MATLAB enables rapid synthesis of a
stable and safe digital controller for such plants without switching the
environment.

>>>>

\begin{abstract}
%
We present an automated MATLAB Toolbox, named \emph{DSSynth} (Digital-System
Synthesizer), to synthesize sound digital controllers for physical plants
that are represented as linear time-invariant systems with single input and
output.  In~particular, DSSynth synthesizes digital controllers that are
sound w.r.t.~stability and safety specifications.  DSSynth considers the
complete range of approximations, including time discretization,
quantization effects and finite-precision arithmetic (and its rounding
errors).  We demonstrate the practical value of
this toolbox by automatically synthesizing stable and safe controllers for intricate
physical plant models from the digital control literature.
The resulting toolbox enables the application of program synthesis
to real-world control engineering problems.
%
\end{abstract}

@@

Control theory targets the construction of reliable systems by providing
mathematical guarantees about the stability and the desired performance of
closed-loop dynamics, where outputs of discrete plant $G(z)$ are fed back
and compared to a reference signal towards which a controller $C(z)$ should
steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
depicts a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System}
\label{fig:typical-control-system}
\end{figure}

@@

The present tool paper addresses this limitation and describes a MATLAB
toolbox for DSSynth.  MATLAB is very commonly used for modeling physical
plants.  Thus, the integration into MATLAB enables rapid synthesis of a
stable and safe digital controller for such plants without switching the
environment. Experimental results show that \tool is able to efficiently 
synthesize stable and safe controllers for a set of intricate benchmarks taken 
from the literature:  the median runtime for our benchmarks set is $124$\,s, 
and the average synthesis time amounts to $35.5$\,s for closed-loop control 
systems represented by state-space equations, while for transfer functions, the average synthesis
time amounts to $123.6$\,s.
